\documentclass[a4paper,12pt]{article}

% Packages
\usepackage[utf8]{inputenc}   % Encoding of input text
\usepackage{amsmath}          % For mathematical formulas
\usepackage{amsfonts}         % For mathematical fonts
\usepackage{amssymb}          % For mathematical symbols
\usepackage{graphicx}         % For including graphics
\usepackage{geometry}         % To adjust page margins
\usepackage{fancyhdr}         % For header and footer customization
\usepackage{hyperref}         % For hyperlinks

% Page layout
\geometry{left=1in, right=1in, top=1in, bottom=1in}

% Header and Footer
\pagestyle{fancy}
\fancyhead[L]{Data Estimation}  % Left header
\fancyhead[C]{Abhinav I S}         % Center header
\fancyhead[R]{\today}              % Right header
\fancyfoot[C]{\thepage}          % Center footer with page number

% Title
\title{Assignment 3 : Data Estimation}
\author{Abhinav I S, EE23B002}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
    
\end{abstract}

\section{Introduction}
% Introduction content
The data given to us in the experiments, corresponds to the spectral radiance per 
unit wavelength. We are expected to estimate the various parameters by curve fitting
this data. 

The equation for spectral radiance per unit wavelength is given by

$$
B_{\lambda}(\lambda, T) = \frac{2 h c^{2}}{\lambda^{5}} \frac{1}{e^{\frac{h \nu}{k_{B} T}}-1}
$$

\section{Methodology}
% Methodology content
\subsection{Plotting}
I begin by plotting each dataset given to us, this can be done by running
the corresponding codeblocks in the notebook

\section{Results}
% Results content
Present the findings of your assignment. Use tables, figures, and charts if necessary to illustrate your results.

\section{Discussion}
% Discussion content
Discuss the implications of your results. Interpret the findings and relate them to your objectives.

\section{Conclusion}
% Conclusion content
Summarize the main points of your assignment and any conclusions you have drawn.

\section{References}
% References content
Include all the sources you referenced in your assignment. Use the appropriate citation style as required by your assignment guidelines.

% Bibliography (if you are using BibTeX, uncomment this)
% \bibliographystyle{plain}
% \bibliography{references}

\end{document}
